### 2020-11-09 reports/article.tex
last corrections - version submitted to biorxiv

% title goes here:
\begin{flushleft}
{\Large Spatially-explicit simulation of urban heat mitigation by increasing the tree canopy cover
\textbf\newline{}
}
\newline
% authors go here:
\\
Mart\'i Bosch\textsuperscript{1,*},
Maxence Locatelli\textsuperscript{1},
Perrine Hamel\textsuperscript{2},
R\'emi Jaligot\textsuperscript{1},
J\'er\^ome Chenal\textsuperscript{1},
St\'ephane Joost\textsuperscript{3}
\\
\bigskip
\bf{1} Urban and Regional Planning Community, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland
\\ 
\bf{2} Asian School of the Environment, Nanyang Technological University, Singapore
\\
\bf{3} Laboratory of Geographic Information Systems, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland
\\
\bigskip
\bf{*} Corresponding author: marti.bosch@epfl.ch

@@

% Urban green space, especially trees, can contribute to the reduction of urban temperatures in extreme heat events.
Urban green infrastructure, especially trees, are widely regarded as one of the most effective ways to reducing urban temperatures in extreme heat events, and alleviate its adverse impacts on human health and well-being.
% Nevertheless, the effect of the spatial pattern on urban temperatures.
Nevertheless, urban planners and decision-makers are still lacking methods and tools to spatially assess the cooling effects of urban green spaces and exploit them to assess greening strategies at the urban agglomeration scale.
This article introduces a novel spatially-explicit approach to simulate urban greening scenarios by increasing the tree canopy cover in the existing urban fabric, and evaluating their heat mitigation potential.
The latter is achieved by applying the InVEST urban cooling model to the synthetic land use/land cover maps generated for the greening scenarios.
An case study in the urban agglomeration of Lausanne, Switzerland, experiments with a range of tree canopy increases in distinct spatial configurations, and shows a potential alleviation of the urban nighttime temperatures of up to 2$\degree$C.
The spatial pattern of the tree canopy strongly influences the human exposure to the highest temperatures, and small increases in the abundance of tree canopy cover with the appropriate spatial configuration can have major impacts on human health and well-being.
% This article
The proposed approach can serve to support urban planning and design adaptative solutions to enhance climate resilience.

@@

% To that end, cities are increasingly
Increasing urban green space, especially the urban tree canopy, has been one of the most widely advocated strategies of urban heat mitigation, nevertheless, the impacts of the urban tree canopy on air temperature show a complex spatial behaviour that remains poorly understood \cite{bowler2010urban,phelan2015urban,koc2018evaluating}.
% Therefore, there is an urgent need to develop robust and spatially explicit methods to quantify the contribution of urban green space to urban heat mitigation \cite{haaland2015challenges,artmann2019urban}.
% Therefore, the extent to which cities can use green infrastructure to reduce heat stress remains uncertain.
% TODO: While many case studies have reproted strong evidence of the heat mitigation of urban green space, e.g., cooling effects of parks, very few studies have attempted to model such effects in space so that synthetic scenarios can be evaluated
% TODO: from the ecosystem service perspective, there is a need to consider green space development for the entire urban region \cite{lin2013sharing,haaland2015challenges,artmann2019urban}
While many case studies have reported evidence of the cooling effects of urban green areas, the relationship between their size and their cooling capacity is non-linear \cite{zardo2017estimating}, and little is known about how the overall spatial configuration of urban green spaces affects the heat mitigation at the urban agglomeration scale \cite{lin2013sharing,jim2013sustainable,haaland2015challenges,artmann2019urban}.
% TODO: case studies might be hard to generalize, e.g., effects of the background climate \cite{zhou2017effects}, \cite{yu2018strong,wang2020significant}.
% Additionally, the effects configuration of urban green space on heat mitigation are strongly mediated by the background climate of the region of study \cite{zhou2017effects,yu2018strong,wang2020significant}.
% what is the gap that we are addressing: there have not been fine-grained evaluations of the effect of increasing the tree canopy in realistic settings.
Therefore, the extent to which cities can use green infrastructure to reduce heat stress remains uncertain, largely because of the lack of fine-grained approaches to evaluate the cooling effects of the spatial pattern of the tree canopy at the urban agglomeration scale. % , which consider the existing urban fabric and local environmental context.

% The present work introduces a novel spatially-explicit method to evaluate the heat mitigation potential of altering the abundance and spatial configuration of the urban tree canopy cover in realistic settings.
With the aim of addressing the above shortcomings, the present work introduces a novel spatially-explicit method to evaluate the heat mitigation potential of altering the abundance and spatial configuration of the urban tree canopy cover in realistic settings.
The proposed method consists of two major parts.
% 1. Couple the cadastral LULC map with a high-resolution tree canopy map to detect locations where the tree canopy cover can be increased
% 2. Generate a variety of synthetic scenarios by increasing the tree canopy cover, which can mimic urban greening strategies. % in different spatial configurations
% 3.
% First, a land use/land cover map is coupled with a high-resolution tree canopy map to detect candidate pixels where the tree canopy cover can be increased.
% Secondly, a synthetic scenario is generated by increasing the tree canopy cover in a fraction of the candidate pixels --- the quantity of transformed pixels can be set exogenously, e.g., to mimic available budgets and resources.
% The transformed pixels can be selected from the candidate pixels by randomly sampling, or pursuing specific spatial configurations by scattering or clustering them to other pixels with high tree canopy cover.
% % Finally, the synthetic LULC map of each scenario is fed to the InVEST urban cooling model in order to estimate the air temperature of
% Finally, the spatial distribution of air temperature of each scenario is estimated by applying the InVEST urban cooling model to the corresponding synthetic LULC map.
% Given the candidate locations where the tree canopy can be increased, which can be mapped from land use/land cover (LULC) data and high-resolution tree canopy maps, a set
% First, given the candidate locations where the tree canopy can be increased in an existing urban fabric,
First, synthetic scenarios are generated by increasing the tree canopy cover in candidate locations where the existing urban fabric permits it. % In order to explore the effects of the abundance and A set of 
% is applied with the LULC map that corresponds to
Then, the spatial distribution of air temperature of each synthetic scenario is estimated with the InVEST urban cooling model, which simulates urban heat mitigation based on three biophysical processes, namely shade, evapotranspiration and albedo. % which simulates urban heat mitigation based on the shade, evapotranspiration and albedo of the urban fabric.
By applying such a procedure in the urban agglomeration of Lausanne, Switzerland, this study aims to map the heat mitigation potential that can be achieved departing from the existing urban fabric.
In order to quantify the effects of the abundance and spatial configuration of the tree canopy cover on urban heat mitigation, a set of synthetic scenarios are generated by increasing different proportions of tree canopy cover in distinct spatial configurations. % and human thermal comfort
% The latter is achieved by coupling a gridded population census with the temperature maps simulated with different proportions and spatial configurations of tree canopy cover.
Additionally, the human exposure to urban heat is evaluated in each scenario by coupling the simulated temperature map with a gridded population census.
% TODO: the aim is to do something that helps planning
% The results

@@

The parameters of the model have been set based on its calibration to the same study area by Bosch et al. \cite{bosch2020spatially}.
Finally, the rural reference temperature ($T_{ref}$) and UHI magnitude ($UHI_{max}$) values have been set based on the air temperature of 11 monitoring stations in the study area (see \autoref{fig:monitoring-stations}). More precisely, $T_{ref}$ has been set as the 9 p.m. air temperature measurement --- the moment of maximal UHI intensity in Switzerland \cite{burgst2019representing} --- of the station showing the lowest temperature value, and $UHI_{max}$ has been set as the difference between the 9 p.m. temperature measurement of the station showing the highest temperature value and $T_{ref}$.
% Given that the UHI effect in Switzerland reaches its maximal intensity around 9 p.m. \cite{burgst2019representing}, this study evaluates it based on the air temperature observations of that hour.
With the above definitions, a reference day for the simulations has been selected from the 2018-2019 period as the day showing the maximum $UHI_{max}$ with $T_{ref} > 20$. Such a date corresponds to July 27$^{th}$ 2018, with $T_{ref} = 20.60 \degree C$ and $UHI_{max} = 7.38 \degree C$.

@@

% \subsubsection*{Mapping candidate pixels}  %  where the tree canopy cover can be increased
% One of the main advantages of using models based on biophysical mechanisms is that they allow for reasonable
% Departing from the refined LULC map, a set of synthetic scenarios will be simulated by altering the LULC classes of certain pixels in a way that corresponds to reasonable transformations that could occcur in urban areas.
% More precisely, in order to mimic scenarios of urban greening, pixels whose base LULC class corresponds to roads, sidewalks, traffic islands and other impervious surfaces will be changed to the LULC code that has the same base class but with the highest tree cover, e.g.,  pixels of a post-refinement class ``sidewalk with low tree/low building cover'' would be changed to ``sidewalk with high tree/low building cover''.
Departing from the refined LULC map, a set of urban greening scenarios will be simulated by altering the LULC classes of certain candidate pixels in a way that corresponds to reasonable transformations that could occcur in urban areas.
More precisely, pixels whose base LULC class corresponds to ``building'', ``road, path'', ``sidewalk'', ``traffic island'', ``other impervious'' and ``garden'' are changed to the LULC code that has the same base class but with the highest tree cover, e.g.,  pixels of a post-refinement class ``sidewalk with low tree/low building cover'' are be changed to ``sidewalk with high tree/low building cover''.
% limit such that the proportion of tree canopy cover and the proportion of building cover (i.e., "shade" + "bulding_intensity") does not amount to more than 100\%
In order to ensure that such an increase of the tree canopy cover is performed only where the existing urban fabric permits it, pixels might only be transformed when two conditions are met.
% First, the transformations might only take place in pixels where the proportion of building cover is under 25\%, i.e., there is a 75\% of the pixel area which could be occupied by a tree crown.
First, the proportion of building cover in the candidate pixels must be under 25\%, i.e., there is a 75\% of the pixel area which could be occupied by a tree crown.
% \footnote{Following the advice given by the directorate of resoures and natural heritage in the Canton of Vaud (DGE-DIRNA), the threshold over which a pixel is considered to have a high tree canopy cover has been set to 75\%, which corresponds to placing trees of a spheric crown with a 5~m radius spaced 10~m from one another so that they form a continuous canopy.}
Secondly, pixels of the ``road, path'' class might only be transformed when they are adjacent to a pixel of a different class, which prevents increasing the tree canopy cover in pixels that are in the middle of a road (e.g., a highway).

% \subsubsection*{}
% With the aim of evaluating the effect of both the abundance and spatial configuration of the tree canopy cover on air temperature, a collection of scenarios is generated as follows.
% After mapping the candidate pixels where the tree canopy cover can be increased, a collection of scenarios is generated in order to evaluate the effect of both the abundance and spatial configuration of the tree canopy cover on air temperature.
% a set of scenarios is generated by transforming a 25, 50, 75 and 100\% of the pixels where the tree canopy cover can be increased.
% Each scenario is characterized by two key features, i.e., the proportion of candidate pixels where the tree canopy is increased
After mapping the candidate pixels where the tree canopy cover can be increased, a scenario can be generated with two key parameters, i.e., the overall proportion of candidate pixels where the tree canopy is actually increased, and the way in which the candidate pixels where such a transformation occurs are spatially sampled.
In order to evaluate the effect of the abundance of tree canopy cover on air temperature, a set of scenarios is generated by transforming a 12.5, 25, 37.5, 50, 62.5, 75 and 87.5\% of the candidate pixels respectively.
For each of the foregoing proportions, three distinct approaches to spatially sample from the candidate pixels are used. The first consists in randomly sampling from the candidate pixels until the desired proportion of changed pixels is matched.
In the second and third approaches, the candidate pixels are sampled according to the number of pixels with high tree canopy cover (i.e., greater than 75\%) found in their Moore neighborhood, that is, in the second approach, pixels with higher number of high tree canopy cover neighbors are transformed first, which intends to spatially cluster pixels of high tree canopy cover, whereas the third approach intends to spatially scatter pixels of high tree canopy cover by giving precedence to pixels with lower number of high tree canopy neighbors.
% The final collection of scenarios is generated by transforming a 12.5, 25, 37.5, 50, 62.5, 75 and 87.5 of the candidate pixels.
Given that the three sampling approaches are stochastic, for each scenario configuration, i.e., each pair of proportion of transformed candidate pixels and sampling approach, the corresponding temperature maps will be computed by averaging a number of simulation runs. 
After observing little variability among the simulation results, the number of runs of a each configuration has been set to 10.
Lastly, the set of scenarios is completed with a configuration where a 100\% of the candidate pixels are transformed, which is independent of the sampling approach or scenario run since there exists a single deterministic way to transform all the candidate pixels.
The final number of scenarios simulated scenarios is 211, i.e., 10 scenario runs for 3 different sampling approaches and 7 proportions of transformed candidate pixels, plus a last scenario where all the pixels are transformed.

@@

The relationship between the number of transformed candidate pixels by their original LULC class and the overall proportion of transformed candidate pixels is shown in \autoref{fig:scenario-lulc-barplot}.
\begin{figure}
  \centering
  \includegraphics[width=.6\textwidth]{figures/scenario-lulc-barplot}%
  \caption{\label{fig:scenario-lulc-barplot} Number of transformed pixels by its original LULC class for an overall proportion of transformed pixels of 25, 50, 75 and 100\%. The lines at the top of the bars represent the 95\% confidence intervals. The bar heights and the confidence intervals are computed out of all the simulation runs and sampling approaches. See the Jupyter Notebook at \hyperref[sec:si-scenarios]{section S2.1} for the detailed numbers of the figure.}
\end{figure}
Changing a 25, 50, 75 and 100\% of the candidate pixels corresponds to a total number of pixels changed of 118880, 237760, 356640 and 475520 respectively.
In the latter case, i.e., increasing the tree canopy in all the possible pixels, a 61.50\% of the pixels correspond to the ``garden'' LULC class, followed by ``road, path'', ``building'', ``other impervious'', which account for a a 18.01, 10.81 and 7.69\% respectively. Finally, the LULC classes of ``sidewalk'' and ``traffic island'' constitute only a 1.67 and 0.3\% of the  pixels where the tree canopy can be increased.
% changing a 25, 50, 75 and 100\% of the potential pixels corresponds to a total number of pixels changed of 118880, 237760, 356640 and 475520 respectively.
% On average over all the simulation runs and sampling approaches,
The differences when considering the sampling approaches separately are small relative to the total number of transformed candidate pixels.
The largest differences between sampling approaches can be noted in the number of transformed pixels that originally belong to the ``garden'' class.
% which the clustering approach consistently transforms a larger share of pixels of the ``garden''
When transforming a 25, 50 and 75\% of the candidate pixels, clustering respectively transforms (on average among the simulation runs) a 0.90, 0.38 and 0.12\% more garden pixels than random sampling, and a 1.28, 0.76 and 0.43\% more garden pixels than the scattering approach (\autoref{fig:scenario-lulc-barplot-comparison}). 
\begin{figure}
  \begin{adjustwidth}{-.4\textwidth}{0cm}  
    \centering
    \includegraphics[width=\linewidth]{figures/scenario-lulc-barplot-comparison}
    \caption{\label{fig:scenario-lulc-barplot-comparison} Effect of the sampling approach on the number of transformed pixels by its original LULC class for an overall proportion of transformed pixels of 25, 50 and 75\%. The lines at the top of the bars represent the 95\% confidence intervals. The bar heights and the confidence intervals are computed out of all the simulation runs. See the Jupyter Notebook at \hyperref[sec:si-scenarios]{section S2.1} for the detailed numbers of the figure.}
  \end{adjustwidth}
\end{figure}

@@

@@

The relationships between the landscape metrics of each scenario run and the corresponding simulated average temperature $\overline{T}$ (over all the pixels) are displayed in \autoref{fig:scenario-metrics}.
\begin{figure}
  \begin{adjustwidth}{-.4\textwidth}{0cm}  
    \includegraphics[width=.99\linewidth]{figures/scenario-metrics}
    % \captionsetup{width=\linewidth, margin={0cm,-.4\textwidth}}
    \caption{\label{fig:scenario-metrics} Relationship between landscape metrics and the simulated average temperature $\overline{T}$ for each scenario run, colored to distinguish the sampling approaches. See the Jupyter Notebook at \hyperref[sec:si-scenario-metrics]{section S2.2} for the detailed numbers of the figure.}
  \end{adjustwidth}
\end{figure}
% The values of PLAND, which are directly related to the proportion of tranformed candidate pixesl
The proportion of landscape (PLAND) occupied by pixels with high tree canopy cover range from 17.26 to 53.37\%. As a composition metric, PLAND is directly related to the proportion of transformed candidate pixels, and the start and end of the PLAND value range correspond to transforming 0 and 100\% of the candidate pixels respectively.
The relationship between PLAND and the average simulated temperature of each scenario $\overline{T}$ shows a sharp monotonic decrease. However, for the same PLAND values, clustering the transformed pixels to other pixels with high tree canopy cover consistently leads to higher $\overline{T}$ than scattering or randomly sampling --- the latter approaches show almost indistinguishable PLAND and $\overline{T}$ relationship.
% With the exception of the mean shape index,

>>>>

% title goes here:
\begin{flushleft}
  {
    % \Large Spatially-explicit simulation of urban heat mitigation by increasing the tree canopy cover
    % \Large Targeted urban greening strategies for urban heat mitigation: a spatially-explicit approach
    \Large Evaluating urban greening scenarios for urban heat mitigation: a spatially-explicit approach
    \textbf\newline{}
  }
  \newline
  % authors go here:
  \\
  Mart\'i Bosch\textsuperscript{1,*},
  Maxence Locatelli\textsuperscript{1},
  Perrine Hamel\textsuperscript{2},
  R\'emi Jaligot\textsuperscript{1},
  J\'er\^ome Chenal\textsuperscript{1},
  St\'ephane Joost\textsuperscript{3,1}
  \\
  \bigskip
  \bf{1} Urban and Regional Planning Community, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland
  \\ 
  \bf{2} Asian School of the Environment, Nanyang Technological University, Singapore
  \\
  \bf{3} Laboratory of Geographic Information Systems, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland
  \\
  \bigskip
  \bf{*} Corresponding author: marti.bosch@epfl.ch

@@

% Urban green space, especially trees, can contribute to the reduction of urban temperatures in extreme heat events.
Urban green infrastructure, especially trees, are widely regarded as one of the most effective ways to reducing urban temperatures in extreme heat events, and alleviate its adverse impacts on human health and well-being.
% Nevertheless, the effect of the spatial pattern on urban temperatures.
Nevertheless, urban planners and decision-makers are still lacking methods and tools to spatially evaluate the cooling effects of urban green spaces and exploit them to assess greening strategies at the urban agglomeration scale.
This article introduces a novel spatially-explicit approach to simulate urban greening scenarios by increasing the tree canopy cover in the existing urban fabric, and evaluating their heat mitigation potential.
The latter is achieved by applying the InVEST urban cooling model to the synthetic land use/land cover maps generated for the greening scenarios.
% A case study in the urban agglomeration of Lausanne, Switzerland, experiments with a range of tree canopy increases in distinct spatial configurations, and shows a potential alleviation of the urban nighttime temperatures of up to 2$\degree$C.
A case study in the urban agglomeration of Lausanne, Switzerland, illustrates the development of tree canopy scenarios following distinct spatial distribution strategies.
The spatial pattern of the tree canopy strongly influences the human exposure to the highest temperatures, and small increases in the abundance of tree canopy cover with the appropriate spatial configuration can have major impacts on human health and well-being.
% This article
The proposed approach supports urban planning and the design of nature-based solutions to enhance climate resilience.

@@

% To that end, cities are increasingly
Increasing urban green space, especially the urban tree canopy, has been one of the most widely advocated strategies of urban heat mitigation. Nevertheless, the impacts of the urban tree canopy on air temperature show a complex spatial behaviour that remains poorly understood \cite{bowler2010urban,phelan2015urban,koc2018evaluating}.
% Therefore, there is an urgent need to develop robust and spatially explicit methods to quantify the contribution of urban green space to urban heat mitigation \cite{haaland2015challenges,artmann2019urban}.
% Therefore, the extent to which cities can use green infrastructure to reduce heat stress remains uncertain.
% TODO: While many case studies have reproted strong evidence of the heat mitigation of urban green space, e.g., cooling effects of parks, very few studies have attempted to model such effects in space so that synthetic scenarios can be evaluated
% TODO: from the ecosystem service perspective, there is a need to consider green space development for the entire urban region \cite{lin2013sharing,haaland2015challenges,artmann2019urban}
While many case studies have reported evidence of the cooling effects of urban green areas, the relationship between their size and their cooling capacity is non-linear \cite{zardo2017estimating}, and little is known about how the overall spatial configuration of urban green spaces affects the heat mitigation at the urban agglomeration scale \cite{lin2013sharing,jim2013sustainable,haaland2015challenges,artmann2019urban}.
% TODO: case studies might be hard to generalize, e.g., effects of the background climate \cite{zhou2017effects}, \cite{yu2018strong,wang2020significant}.
% Additionally, the effects configuration of urban green space on heat mitigation are strongly mediated by the background climate of the region of study \cite{zhou2017effects,yu2018strong,wang2020significant}.
% what is the gap that we are addressing: there have not been fine-grained evaluations of the effect of increasing the tree canopy in realistic settings.
Therefore, the extent to which cities can use green infrastructure to reduce heat stress remains uncertain, largely because of the lack of fine-grained approaches to evaluate the cooling effects of the spatial pattern of the tree canopy at the urban agglomeration scale. % , which consider the existing urban fabric and local environmental context.

% The present work introduces a novel spatially-explicit method to evaluate the heat mitigation potential of altering the abundance and spatial configuration of the urban tree canopy cover in realistic settings.
With the aim of addressing the above shortcomings, the present work introduces a novel spatially-explicit method to evaluate the heat mitigation potential of altering the abundance and spatial configuration of the urban tree canopy cover in realistic settings.
The proposed method consists of two major parts.
% 1. Couple the cadastral LULC map with a high-resolution tree canopy map to detect locations where the tree canopy cover can be increased
% 2. Generate a variety of synthetic scenarios by increasing the tree canopy cover, which can mimic urban greening strategies. % in different spatial configurations
% 3.
% First, a land use/land cover map is coupled with a high-resolution tree canopy map to detect candidate pixels where the tree canopy cover can be increased.
% Secondly, a synthetic scenario is generated by increasing the tree canopy cover in a fraction of the candidate pixels --- the quantity of transformed pixels can be set exogenously, e.g., to mimic available budgets and resources.
% The transformed pixels can be selected from the candidate pixels by randomly sampling, or pursuing specific spatial configurations by scattering or clustering them to other pixels with high tree canopy cover.
% % Finally, the synthetic LULC map of each scenario is fed to the InVEST urban cooling model in order to estimate the air temperature of
% Finally, the spatial distribution of air temperature of each scenario is estimated by applying the InVEST urban cooling model to the corresponding synthetic LULC map.
% Given the candidate locations where the tree canopy can be increased, which can be mapped from land use/land cover (LULC) data and high-resolution tree canopy maps, a set
% First, given the candidate locations where the tree canopy can be increased in an existing urban fabric,
First, synthetic scenarios are generated by increasing the tree canopy cover in candidate locations where the existing urban fabric permits it. % In order to explore the effects of the abundance and A set of 
% is applied with the LULC map that corresponds to
Then, the spatial distribution of air temperature of each synthetic scenario is estimated with the InVEST urban cooling model, which simulates urban heat mitigation based on three biophysical processes, namely shade, evapotranspiration and albedo. % which simulates urban heat mitigation based on the shade, evapotranspiration and albedo of the urban fabric.
% Additionally, the human exposure to urban heat is evaluated in each scenario by coupling the simulated temperature map with a gridded population census.
Finally, the simulated temperature map is coupled with a gridded population census in order to evaluate the human exposure to urban heat in the scenario.
By applying such a procedure in the urban agglomeration of Lausanne, Switzerland, this study aims to map the heat mitigation potential that can be achieved starting from the existing urban fabric.
With the aim of quantifying the effects of the abundance and spatial configuration of the tree canopy cover on urban heat mitigation, a set of synthetic scenarios are generated by increasing different proportions of tree canopy cover in distinct spatial configurations. % and human thermal comfort
% The latter is achieved by coupling a gridded population census with the temperature maps simulated with different proportions and spatial configurations of tree canopy cover.
% Additionally, the human exposure to urban heat is evaluated in each scenario by coupling the simulated temperature map with a gridded population census.
% The results 
% TODO: similar studies in the region
% In another study on the mitigation of the urban heat island in Lausanne, Labedens et al. \cite{labedens2018modeling}
% In a study of impact of densification on the urban climate of the Lausanne area, Labedens et al. \cite{labedens2018modeling} explore heat mitigation strategies and determine that green roofs, vegetal walls and the increase of the albedo of the building materials can partially mitigate the impact of future urban densification, especially at nighttime.
% In a study of heat mitigation strategies in the Lausanne area, Labedens et al. \cite{labedens2018modeling} use a mesoscale numerical model to evaluate a set of future scenarios. Their results suggest that while the projected urban densification leads to higher temperatures, such an effect can be significantly alleviated with the use of green roofs, vegetal walls and especially the increase of the albedo of the building materials.
% The present article explores a complementary approach
% The approach of this article foucses on the

@@

The parameters of the model are set based on its calibration to the same study area in previous work \cite{bosch2020spatially}.
Finally, the rural reference temperature ($T_{ref}$) and UHI magnitude ($UHI_{max}$) values are derived from the air temperature of 11 monitoring stations in the study area (see \autoref{fig:monitoring-stations}). More precisely, $T_{ref}$ is set as the 9 p.m. air temperature measurement --- the moment of maximal UHI intensity in Switzerland \cite{burgst2019representing} --- of the station showing the lowest temperature value, and $UHI_{max}$ is set as the difference between the 9 p.m. temperature measurement of the station showing the highest temperature value and $T_{ref}$.
% Given that the UHI effect in Switzerland reaches its maximal intensity around 9 p.m. \cite{burgst2019representing}, this study evaluates it based on the air temperature observations of that hour.
With the above definitions, a reference day for the simulations has been selected from the 2018-2019 period as the day showing the maximum $UHI_{max}$ with $T_{ref} > 20$. Such a date corresponds to July 27$^{th}$ 2018, with $T_{ref} = 20.60 \degree C$ and $UHI_{max} = 7.38 \degree C$.

@@

% \subsubsection*{Mapping candidate pixels}  %  where the tree canopy cover can be increased
% One of the main advantages of using models based on biophysical mechanisms is that they allow for reasonable
% Departing from the refined LULC map, a set of synthetic scenarios will be simulated by altering the LULC classes of certain pixels in a way that corresponds to reasonable transformations that could occcur in urban areas.
% More precisely, in order to mimic scenarios of urban greening, pixels whose base LULC class corresponds to roads, sidewalks, traffic islands and other impervious surfaces will be changed to the LULC code that has the same base class but with the highest tree cover, e.g.,  pixels of a post-refinement class ``sidewalk with low tree/low building cover'' would be changed to ``sidewalk with high tree/low building cover''.
Starting from the refined LULC map, a set of urban greening scenarios are generated by altering the LULC classes of certain candidate pixels in a way that corresponds to reasonable transformations that could occcur in urban areas.
More precisely, pixels whose base LULC class corresponds to ``building'', ``road, path'', ``sidewalk'', ``traffic island'', ``other impervious'' and ``garden'' are changed to the LULC code that has the same base class but with the highest tree cover, e.g.,  pixels of a post-refinement class ``sidewalk with low tree/low building cover'' are be changed to ``sidewalk with high tree/low building cover''.
% limit such that the proportion of tree canopy cover and the proportion of building cover (i.e., "shade" + "bulding_intensity") does not amount to more than 100\%
In order to ensure that such an increase of the tree canopy cover is performed only where the existing urban fabric permits it, pixels might only be transformed when two conditions are met.
% First, the transformations might only take place in pixels where the proportion of building cover is under 25\%, i.e., there is a 75\% of the pixel area which could be occupied by a tree crown.
First, the proportion of building cover in the candidate pixels must be under 25\%, i.e., there is a 75\% of the pixel area which could be occupied by a tree crown.
% \footnote{Following the advice given by the directorate of resoures and natural heritage in the Canton of Vaud (DGE-DIRNA), the threshold over which a pixel is considered to have a high tree canopy cover has been set to 75\%, which corresponds to placing trees of a spheric crown with a 5~m radius spaced 10~m from one another so that they form a continuous canopy.}
Secondly, pixels of the ``road, path'' class might only be transformed when they are adjacent to a pixel of a different class, which prevents increasing the tree canopy cover in pixels that are in the middle of a road (e.g., a highway).

% \subsubsection*{}
% With the aim of evaluating the effect of both the abundance and spatial configuration of the tree canopy cover on air temperature, a collection of scenarios is generated as follows.
% After mapping the candidate pixels where the tree canopy cover can be increased, a collection of scenarios is generated in order to evaluate the effect of both the abundance and spatial configuration of the tree canopy cover on air temperature.
% a set of scenarios is generated by transforming a 25, 50, 75 and 100\% of the pixels where the tree canopy cover can be increased.
% Each scenario is characterized by two key features, i.e., the proportion of candidate pixels where the tree canopy is increased
% After mapping the candidate pixels where the tree canopy cover can be increased, a scenario can be generated with two key attributes, i.e., the overall proportion of candidate pixels where the tree canopy is actually increased, and the way in which the candidate pixels where such a transformation occurs are spatially sampled.
After mapping the candidate pixels where the tree canopy cover can be increased, scenarios are generated based on two key attributes: the extent of tree canopy conversion (expressed as a proportion of the total number of candidate pixels), and the selection of pixels to be converted.
% In order to evaluate the effect of the abundance of tree canopy cover on air temperature, a set of scenarios is generated by transforming a 12.5, 25, 37.5, 50, 62.5, 75 and 87.5\% of the candidate pixels respectively.
A set of scenarios is generated by transforming a 12.5, 25, 37.5, 50, 62.5, 75 and 87.5\% of the candidate pixels respectively.
For each of these canopy areas, three distinct selection approaches are used. The first consists in randomly sampling from the candidate pixels until the desired proportion of changed pixels is matched.
In the second and third approaches, the candidate pixels are sampled according to the number of pixels with high tree canopy cover (i.e., greater than 75\%) found in their Moore neighborhood (i.e., the 8 adjacent pixels). In the second approach, pixels with higher number of high tree canopy cover neighbors are transformed first, which intends to spatially cluster pixels of high tree canopy cover.
The third approach intends to spatially scatter pixels of high tree canopy cover by prioritizing pixels with lower number of high tree canopy neighbors.
% The final collection of scenarios is generated by transforming a 12.5, 25, 37.5, 50, 62.5, 75 and 87.5 of the candidate pixels.
Given that the three sampling approaches are stochastic, for each scenario configuration, i.e., each pair of proportion of transformed candidate pixels and sampling approach, the corresponding temperature maps will be computed by averaging a number of simulation runs. 
After observing little variability among the simulation results, the number of runs of a each configuration has been set to 10.
Lastly, the set of scenarios is completed with a configuration where a 100\% of the candidate pixels are transformed, which is independent of the sampling approach or scenario run since there exists a single deterministic way to transform all the candidate pixels.
The final number of scenarios simulated scenarios is 211, i.e., 10 scenario runs for 3 different sampling approaches and 7 proportions of transformed candidate pixels, plus a last scenario where all the pixels are transformed.

@@

The relationship between the number of transformed candidate pixels by their original LULC class and the overall proportion of transformed candidate pixels is shown in \autoref{fig:scenario-lulc-barplot}.
Changing a 25, 50, 75 and 100\% of the candidate pixels corresponds to a total number of pixels changed of 118880, 237760, 356640 and 475520, which account for a total area of 1188.8, 2377.6, 3566.4 and 4755.2 hectares respectively.
In the latter case, i.e., increasing the tree canopy in all the possible pixels, 61.50\% of the pixels correspond to the ``garden'' LULC class, followed by ``road, path'', ``building'', ``other impervious'', (18.01, 10.81 and 7.69\%, respectively). Finally, the LULC classes of ``sidewalk'' and ``traffic island'' constitute only 1.67 and 0.3\% of the  pixels where the tree canopy can be increased.
% changing a 25, 50, 75 and 100\% of the potential pixels corresponds to a total number of pixels changed of 118880, 237760, 356640 and 475520 respectively.
% On average over all the simulation runs and sampling approaches,
The differences when considering the sampling approaches separately are small relative to the total number of transformed candidate pixels.
The largest differences between sampling approaches can be noted in the number of transformed pixels that originally belong to the ``garden'' class.
% which the clustering approach consistently transforms a larger share of pixels of the ``garden''
When transforming 25, 50 and 75\% of the candidate pixels, clustering respectively transforms (on average among the simulation runs) a 0.90, 0.38 and 0.12\% more garden pixels than random sampling, and 1.28, 0.76 and 0.43\% more garden pixels than the scattering approach (\autoref{fig:scenario-lulc-barplot-comparison}).

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=.6\textwidth]{figures/scenario-lulc-barplot}%
  \caption{\label{fig:scenario-lulc-barplot} Number of transformed pixels by its original LULC class for an overall proportion of transformed pixels of 25, 50, 75 and 100\%. The lines at the top of the bars represent the 95\% confidence intervals. The bar heights and the confidence intervals are computed out of all the simulation runs and sampling approaches. See the Jupyter Notebook at \hyperref[sec:si-scenarios]{section S2.1} for the detailed numbers of the figure.}
\end{figure}

\begin{figure}[H]
  \begin{adjustwidth}{-.4\textwidth}{0cm}  
    \centering
    \includegraphics[width=\linewidth]{figures/scenario-lulc-barplot-comparison}
    \caption{\label{fig:scenario-lulc-barplot-comparison}
      Comparison of between the number of transformed pixels by its original LULC class with the random sampling approach and the scattering ($N_{random} - N_{scatter}$, left subplot) and the clustering ($N_{random} - N_{cluster}$, right subplot) selection approaches, for an overall proportion of transformed pixels of 25, 50 and 75\%.
      The lines at the top of the bars represent the 95\% confidence intervals. The bar heights and the confidence intervals are computed out of all the simulation runs. See the Jupyter Notebook at \hyperref[sec:si-scenarios]{section S2.1} for the detailed numbers of the figure.}
  \end{adjustwidth}
\end{figure}

@@

The relationships between the landscape metrics of each scenario run and the corresponding simulated average temperature $\overline{T}$ (over all the pixels) are displayed in \autoref{fig:scenario-metrics}.
\begin{figure}
  \begin{adjustwidth}{-.4\textwidth}{0cm}  
    \includegraphics[width=.99\linewidth]{figures/scenario-metrics}
    % \captionsetup{width=\linewidth, margin={0cm,-.4\textwidth}}
    \caption{\label{fig:scenario-metrics} Relationship between landscape metrics and the simulated average temperature $\overline{T}$ for each scenario run, colored to distinguish the sampling approaches. See the Jupyter Notebook at \hyperref[sec:si-scenario-metrics]{section S2.2} for the detailed numbers of the figure.}
  \end{adjustwidth}
\end{figure}
% The values of PLAND, which are directly related to the proportion of tranformed candidate pixesl
The proportion of landscape (PLAND) occupied by pixels with high tree canopy cover range from 17.26 to 53.37\%. As a composition metric, PLAND is directly related to the proportion of transformed candidate pixels, and the extreme values of the PLAND range correspond to transforming 0 and 100\% of the candidate pixels respectively.
The relationship between PLAND and the average simulated temperature of each scenario $\overline{T}$ shows a sharp monotonic decrease. However, for the same PLAND values, clustering the transformed pixels to other pixels with high tree canopy cover consistently leads to higher $\overline{T}$ than scattering or randomly sampling --- the latter approaches show almost indistinguishable PLAND and $\overline{T}$ relationship.
% With the exception of the mean shape index,
